---
title: 'MSBA The Median Place Capstone - Digital Viewership Prediction'
author: "Natalia Fadeeva "
date: "January 9, 2020"
output:
  html_document:
    df_print: paged
---

```{r Setup, echo=TRUE, eval=TRUE, results=TRUE, include=TRUE, warning=FALSE, message=FALSE}
#Insall bigrquery to connect to Google Cloud
library(bigrquery)
```


```{r Setup, echo=TRUE, eval=TRUE, results=TRUE, include=TRUE, warning=FALSE, message=FALSE}
# Creating a vector of packages used within
packages <- c('tidyverse',
              'ggplot2',
              'readr',
              'xts',
              'DMwR2',
              'quantmod',
              'TTR',
              'performanceEstimation',
              'nnet',
              'e1071',
              'earth',
              'randomForest',
              'kernlab',
              'RQuantLib',
              'MASS', 
              'car'
              )

# Checking for package installations on the system and installing if not found
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}

# Including the packages for use
for(package in packages){
  library(package, character.only = TRUE)
}
```

##Access combined NBC Digital Linear Data set
```{r Access Combined Digital Linear Data, echo=TRUE, eval=TRUE, results=TRUE, include=TRUE, warning=FALSE, message=FALSE}
# Use capstone project ID here
project <-"capstone-247602"
# Query table
sql<- "SELECT * FROM [combined_digital_linear.tbl_title_matching_stage_3_FINAL]"
comb_dat<-query_exec(sql, project = project, useLegacySql = FALSE)
setwd("~/Capstone")
save(comb_dat, file = "comb_data.csv")
```


```{r Access Combined Digital Linear Data, echo=TRUE, eval=TRUE, results=TRUE, include=TRUE, warning=FALSE, message=FALSE}
#combined_digital_linear <- read_csv("~/Capstone/combined_digital_linear.csv")
comb_dat<- mutate_if(comb_dat, is.character, as.factor)
```
##Detect Outliers
```{r}
## Identify Outliers for average_mins_viewed (Digital viewership)
outliers_min<-boxplot.stats(comb_dat$average_mins_viewed)$out
#print(outliers)
#Find out which rows contain the outlier values for Average Mins Viewed
comb_dat[which(comb_dat$average_mins_viewed %in% outliers_min),]
```
```{r}
##Identify outliers for Imps (Linear Viewership)
outliers_imps<-boxplot.stats(comb_dat$Imps)$out
print(outliers_imps)
#Find out which rows contain the outlier values for Imps
comb_dat[which(comb_dat$Imps %in% outliers_imps),]
```
```{r}
#Remove outliers from the dataset
comb_dat2<- comb_dat[-which(comb_dat$average_mins_viewed %in% outliers_min),]
comb_dat2<- comb_dat2[-which(comb_dat$Imps %in% outliers_imps),]

```
#Remove 'All_Inds' column as it contains many missing values 
```{r}
#comb_dat2<- subset(comb_dat2, select = -c(All_Inds ))
comb_dat2<-comb_dat2[complete.cases(comb_dat2), ]
view(comb_dat2)
```
##Analyze Digital Average Mins Viewed and Imps values
```{r}
summary(comb_dat2$average_mins_viewed)
summary(comb_dat2$Imps)
#boxplot(comb_dat2$average_mins_viewed)
```

#Determine correlations - added the following variables: dummy_weekday, dummy_10pm, dummy_9pm, dummy_8pm, dummy_genre_alt, dummy_genre_com, dummy_genre_dra, and quarter
```{r}
require(ggpubr)
require(corrplot)
library(dplyr)
```
```{r}
cormatrix<-select(comb_dat2, average_mins_viewed, Imps, Median_Age, Median_Income, episode_number, Season, asset_length, dummy_weekday, dummy_10pm, dummy_9pm, dummy_8pm, dummy_genre_alt, dummy_genre_com, dummy_genre_dra, quarter)
#head(cormatrix)
#str(cormatrix)
cor_1 <- round(cor(cormatrix), 2)
#cor_1
corrplot(cor_1, method = "circle")
```
```{r}
#After increasing the number of variables from 7 to 15, the correlation coefficient of average_mins_viewed (digital) and imps(linear) went up from 0.49 to 0.61!

cor.test(comb_dat2$average_mins_viewed, comb_dat2$Imps, method = c("pearson", "kendall", "spearman"))

ggscatter(comb_dat2, x = "Imps", y = "average_mins_viewed",
       add = "reg.line", conf.int = TRUE,
       cor.coef = TRUE, cor.method = "pearson",
       xlab = "Linear impressions", ylab = "Digital average mins viewed",
       title = "Correlation of Linear TV Impessions with Digital Streaming Min")

#ggplot(comb_dat2, aes(x=Imps, y=average_mins_viewed)) + geom_point() + scale_x_continuous #(limits=c(0,20000000)) + labs(x="Linear Impressions", y="Digital Ave Minutes Viewed", #title="Correlation of Linear TV Impessions with Digital Streaming Min")
```
```{r}
## Run Multiple Linear Regression
fit <- lm(average_mins_viewed ~ Imps + Median_Age + Median_Income + episode_number + Season+ asset_length + dummy_weekday + dummy_10pm + dummy_9pm + dummy_8pm + dummy_genre_alt + dummy_genre_com + dummy_genre_dra + quarter, data=comb_dat2)
summary(fit)
#coefficients(fit) # model coefficients
#confint(fit, level=0.95) # CIs for model parameters
#fitted(fit) # predicted values
#residuals(fit) # residuals
#anova(fit) # anova table
#vcov(fit) # covariance matrix for model parameters
#influence(fit) # regression diagnostics
```
##Variable Selection
```{r}
# We perform stepwise selection (forward, backward, both) using the stepAIC( ) function from the MASS package. 
library(MASS)
fit <- lm(average_mins_viewed ~ Imps + Median_Age + Median_Income + episode_number + Season+ asset_length + dummy_weekday + dummy_10pm + dummy_9pm + dummy_8pm + dummy_genre_alt + dummy_genre_com + dummy_genre_dra + quarter, data=comb_dat2)
step <- stepAIC(fit, direction="both")
step$anova # display results
```
# Variable selection using he leaps( ) function from the leaps package. In the following code nbest indicates the number of subsets of each size to report.
```{r}
# All Subsets Regression
library(leaps)
attach(comb_dat2)
leaps<-regsubsets(average_mins_viewed ~ Imps + Median_Age + Median_Income + episode_number + Season+ asset_length + dummy_weekday + dummy_10pm + dummy_9pm + dummy_8pm + dummy_genre_alt + dummy_genre_com + dummy_genre_dra + quarter, data=comb_dat2,nbest=10)
# view results
summary(leaps)
# plot a table of models showing variables in each model.
# models are ordered by the selection statistic.
plot(leaps,scale="r2")
# plot statistic by subset size
library(car)
subsets(leaps, statistic="rsq")
```

